---
title: Conor Higgins' Resume
author: Conor Higgins
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'dd_resume.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results = 'asis',
  echo = FALSE
)

source("CV_printing_functions.R")

CV <- create_CV_object(
  data_location = "./",
  pdf_mode = params$pdf_mode,
  resume_mode = TRUE
)
```


Aside
================================================================================



Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV |> print_contact_info()
```



Technical Skills {#skills}
--------------------------------------------------------------------------------

Highly Skilled & Experienced

- SQL (Snowflake)
- Python
- Snowflake
- AWS
- Docker
- Airflow
- Prefect
- git / CI/CD
- bash
- R
- Looker (LookML)
- dbt

Experience With & Learning

- Terraform
- Kubernetes
- Dagster
- Fivetran
- Tableau / PowerBI


Note {#prior-exp}
--------------------------------------------------------------------------------

*Feel free to [get in touch](mailto:conormjhiggins@gmail.com) for further information on experience and projects prior to 2020.*


More Info {#more-info}
--------------------------------------------------------------------------------

Made w/ [**pagedown**](https://github.com/rstudio/pagedown).

Source code: [github.com/conormjhiggins/cv](https://github.com/conormjhiggins/cv).

Last updated on `r Sys.Date()`.




Main
================================================================================

Conor Higgins {#title}
--------------------------------------------------------------------------------

```{r}
CV <- print_text_block(CV, "intro")
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'education')
```



Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'industry_positions')
```

```{r}
print_links(CV)
```
