---
title: Hannah Banks' Resume"
author: Hannah Banks
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---


```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- TRUE

# Holds all the links that were inserted for placement at the end
links <- c("https://www.linkedin.com/in/hannah-banks-510707216/")

source('parsing_functions.R')


# First let's get the data, filtering to only the items tagged as
# Resume items
position_data <- read_csv2('positions.csv') %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('research_positions', 'industry_positions') ~ 'positions', 
      section %in% c('data_science_writings', 'by_me_press') ~ 'writings',
      TRUE ~ section
    )
  ) 

```


Aside
================================================================================




Contact {#contact}
--------------------------------------------------------------------------------



- <i class="fa fa-envelope"></i> hannah.banks01@yahoo.com
- <i class="fa fa-linkedin"></i> [Hannah Banks](https://www.linkedin.com/in/hannah-banks-510707216/)
- <i class="fa fa-phone"></i> (+44) 7944 407691



Skills {#skills}
--------------------------------------------------------------------------------

Software

- Snapfulfil
- Linnworks
- MACS Software 
- Shopify
- Sorted PRO
- Hubspot
- Amazon Marketplace
- Fulfilled By Amazon
- Zendesk
- Health Roster
- Merlin
- Matchmaker
- Microsoft Suite

Soft Skills

- Communication
- Time Management
- Organisation
- Customer Relationship Building
- Leadership
- Teamwork
- Problem Solving


More Info {#more-info}
--------------------------------------------------------------------------------

Last updated on `r Sys.Date()`.




Main
================================================================================

Hannah Banks {#title}
--------------------------------------------------------------------------------

```{r}
intro_text <- 

"
Relocated to North West England, August 2024

Over the past 5 years, I have worked in varied areas of customer service, developing my skills in all
aspects of relationship building, with a sharp focus on quality, communication and performance. I
pride myself on being able to manage my workload independently as well as working well in a
team. My strengths are in identifying resolutions in the face of issues with professionalism and
efficiency. I have a hands-on approach to all aspects of work, with an enthusiastic can-do attitude."

cat(sanitize_links(intro_text))
```

Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('positions')
```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('education')
```
